\vspace{2in}
\begin{abstract}
\begin{table}
    \begin{tabular}{ll}
    Project Name & : Kinect Assisted Rat Behaviour Analysis for 
    \\
                 &   Experiment Automation

    \\
    Project Team & : Cagri Sofuoglu - Ismet Burak Kadron                                                       	\\
    Term         & : 2014-2                                                                                     	\\
    Keywords     & : Behaviour Analysis, Video Processing, Experiment
    \\
                 &   Automation, Kinect, Depth Data, Data Mining
    \\
    \end{tabular}
\end{table}
Video tracking systems enable behavior to be studied in a reliable and consistent way, and over longer time periods than if they are manually recorded. The system takes an analog video signal, digitizes each frame, and analyses the resultant pixels to determine the location of the tracked animals (as well as other data).Prof. Resit Canbeyli and his fellow researchers at the psychobiology Lab at Bogazici University enlisted our help in building a reliable system with which to track their subjects: rats. This document describes our effort in creating a object tracker for both light and dark environments with the depth data Microsoft Kinect provides. The 2D  depth images are searched for closed contours which are then marked as objects. In our case these objects are the rats Prof. Resit Canbeyli and his co-workers wish to track under all lighting conditions. Here, our progress as of midterm report deadline and planned future work are described.
\end{abstract} 
